testibng

### 2024-01-07 Code/R FIle.qmd
renamed data sets in code
saved data locally

```{r}
# Union Data
tuesdata <- tidytuesdayR::tt_load(2023, week = 36)

demographics <- tuesdata$demographics
wages <- tuesdata$wages
states <- tuesdata$states

# Election Data
tuesdata <- tidytuesdayR::tt_load(2023, week = 45)

house <- tuesdata$house

@@

```{r}
full_data <- states |> 
  filter(sector == "Total") |> 
  left_join(house, by = c("year", "state")) |> 
  filter(party == "DEMOCRAT" | party == "REPUBLICAN") |> 
  mutate(decade = paste0((year - year %% 10), "s"),
         party_binary = ifelse(party == "DEMOCRAT", 0, 1)) 
```

>>>>

```{r}
# Union Data

union_demographics <- read_rds("../Data/union_demographics.rds")
union_wages <- read_rds("../Data/union_wages.rds")
union_states <- read_rds("../Data/union_states.rds")

# Election Data
house <- read_rds("../Data/house.rds")

@@

```{r}
full_data <- union_states |> 
  filter(sector == "Total") |> 
  left_join(house, by = c("year", "state")) |> 
  filter(party == "DEMOCRAT" | party == "REPUBLICAN") |> 
  mutate(decade = paste0((year - year %% 10), "s"),
         party_binary = ifelse(party == "DEMOCRAT", 0, 1))  |> 
  seelect 
```
